%-------------------------
% Resume in Latex
% Author : Gennadii Chursov
% Based off of: https://github.com/sb2nov/resume and https://www.overleaf.com/latex/templates/jakes-resume/syzfjbzwjncs
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{dependencies/latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage[normalem]{ulem}
\usepackage{xcolor}
\usepackage[a4paper,
            left=0.85in,
            right=0.85in,
            top=0.8in,
            bottom=0.8in,
            footskip=0.25in]{geometry}
\input{dependencies/glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
    \item\small{
            {#1 \vspace{-2pt}}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\definecolor{hrefBlue}{RGB}{0,32,96}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
\textbf{\Huge \scshape Dauren Abdykaparov} \\ \vspace{1pt}
\href{tel:447311229998}{+447311229998} $|$
\href{mailto:daurenabd@gmail.com}{\underline{daurenabd@gmail.com}} $|$
\href{https://www.linkedin.com/in/daurenabd/}{\underline{linkedin.com/in/daurenabd/}} $|$
\href{https://github.com/daurenabd}{\underline{github.com/daurenabd}}
\end{center}

%-----------SUMMARY-----------
% \section*{Summary}
% Results-oriented and detail-driven Automation Quality Engineer with a strong background in Java programming and a passion for ensuring software reliability. Experienced in designing, implementing, and executing automated test scripts to verify the functionality and performance of software applications. Proven track record of collaborating with development teams to identify and resolve issues early in the development process. Adept at utilizing testing frameworks such as JUnit and incorporating continuous integration tools like Jenkins. Skilled in creating and maintaining automated test suites for web and mobile applications. Committed to delivering high-quality software by applying industry best practices in testing and automation. Seeking opportunities to contribute technical expertise and enhance software development processes as an Automation Quality Engineer.

%-----------PROGRAMMING SKILLS-----------
% \section{Technical Skills}
% \begin{itemize}[leftmargin=0.15in, label={}]
% \small{\item{
% \textbf{Languages}{: Java, TypeScript, SQL} \\
% \textbf{Frameworks}{: Selenium/Selenide, Playwright, RestAssured, JUnit, TestNG, Cucumber} \\
% \textbf{Developer Tools}{: Git, Docker, Google Cloud Platform, Maven/Gradle, Grafana, Kibana, Splunk} \\
% \textbf{Libraries}{: WireMock, Spring Cloud Contract, Pact, Chaos Monkey}
% }}
% \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart


% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

\resumeSubheading
{Palantir Technologies}{Sep. 2020 -- now}
{Backend Software Engineer working on Foundry, a data management platform.}{London, United Kingdom}
\resumeItemListStart
\resumeItem{
Led the design and implementation of
\href{https://www.palantir.com/docs/foundry/administration/container-governance/}
{\textcolor{hrefBlue}{security controls for Docker containers in Foundry}}
and developed tools for continuous vulnerability scanning and auditing.
This initiative enabled secure,
\href{https://www.palantir.com/docs/foundry/transforms-python/container-overview/}
{\textcolor{hrefBlue}{user-driven container deployment}},
reducing the time from upload to execution
\textbf{from several days to less than 15 minutes}
and removing the need for coordination from Palantir employees.
[Java, Docker, Trivy]
}
\resumeItem {
Developed
\href{https://www.palantir.com/docs/foundry/code-repositories/aip-features/\#code-autocomplete}
{\textcolor{hrefBlue}{a tool similar to GitHub Copilot}},
offering users LLM-generated code completions with support for Foundry-specific code,
resulting in \textbf{50\% reduction} in lead time to production.
}
\resumeItem {
Created
\href{https://www.palantir.com/docs/foundry/transforms-common/local-preview/}
{\textcolor{hrefBlue}{a Gradle plugin}},
allowing users to quickly preview the output by their Spark code on a subset of their input data
without leaving their IDE. This significantly accelerated the development cycle saving
\textbf{more than a minute} per preview, making it on average \textbf{30\% faster}.
[Python, Gradle]
}
\resumeItem {
Achieved \textbf{30x} performance boost for
\href{https://www.palantir.com/docs/foundry/data-lineage/overview/}
{\textcolor{hrefBlue}{Data Lineage}},
one of the most used tools in Foundry that shows a graph of how data flows through the platform,
by decreasing P99 of an endpoint powering it from \textbf{~30s to less than 1s}.
}
\resumeItem {
Automated ElasticSearch (full-text search engine) index migrations for
\href{https://www.palantir.com/docs/foundry/data-integration/application-reference/\#builds}
{\textcolor{hrefBlue}{Job Tracker}},
a tool offering users an overview of code executions run in Foundry.
This unlocked more frequent ES upgrades, \textbf{saved \$250,000 per year} in storage spending alone,
and reduced engineering time required for maintenance of the service down to zero.
}
\resumeItem {
Delivered core backend functionality for
\href{https://www.palantir.com/docs/foundry/maintaining-pipelines/monitoring-views-intro/}
{\textcolor{hrefBlue}{Monitoring at scale}},
a highly scalable data pipeline monitoring tool that replaced multiple ad-hoc solutions.
It allowed users to set up monitoring for entire data pipelines with just a few clicks,
\textbf{saving hours of engineering time} per customer per day,
improving efficiency \& reliability, and minimizing chances of misconfiguration.
[Java]
}
\resumeItem {
As a part of a hack-week competition, implemented backend for an MVP version of
\href{https://www.palantir.com/docs/foundry/hyperauto/overview/}
{\textcolor{hrefBlue}{Palantir HyperAuto}},
a software-defined data integration (SDDI) tool for data systems like Salesforce and SAP\@.
This allowed users to create end-to-end data pipelines based on thousands of datasets
in \textbf{less than 5 minutes}, making a process that would otherwise take days of manual work
more than \textbf{100x faster}.
[Java, SAP]
}
\resumeItem {
Co-authored
\href{https://www.palantir.com/docs/foundry/code-repositories/aip-features/\#ai-error-enhancer}
{\textcolor{hrefBlue}{AI Error Enhancer}},
a \textbf{patented} tool that provides comprehensive error explanations and suggested code changes across Foundry.
This reduced the number of customer-filed support tickets by \textbf{18\%}.
}
\resumeItem {
Wrote
\href{https://www.palantir.com/docs/foundry/}
{\textcolor{hrefBlue}{Palantir's public docs}}
for most of the features mentioned in this document.
}
\resumeItemListEnd

\resumeSubheading
{Skelter Labs}{Mar. 2019 -- Aug. 2020}
{Software Engineer in a conversational AI startup with \$30mil total investment}{Seoul, South Korea}
\resumeItemListStart

\resumeItem {
Achieved \textbf{\#1 rank} in \textit{Korean Question Answering Dataset (KorQuAD)}
with F\textsubscript{1} (standard measure of predictive performance) of \textbf{95.15\%} as of Jan 2020
and in KorQuAD-v2 (similar to v1, but with significantly longer context) with F\textsubscript{1} of
\textbf{88.09\%} as of Jun 2020.
[Python, Tensorflow, GCP]
}
\resumeItem {
Created highly scalable training data pipeline for LLM models, unlocking more frequent experiments.
\newline[Python, Spark, Kubernetes]
}

\resumeItemListEnd

\resumeSubheading
{HENNGE}{Jan. 2019 -- Mar. 2019}
{Software Engineer Intern in a cloud-based security provider with \$225mil market cap}{Tokyo, Japan}
\resumeItemListStart
\resumeItem {
Set up Prometheus, a time-series based monitoring system, for AWS ECS clusters and integrated it with Slack,
achieving \textbf{5x} mean-time-to-acknowledge reduction down to under 3min.
[Terraform, Prometheus, PromQL, AWS]
}
\resumeItemListEnd

\resumeSubheading
{FinApps}{Jan. 2019 -- Mar. 2019}
{Software Engineer working on Torgai, a point-of-sale app for Android}{Almaty, Kazakhstan}
\resumeItemListStart
\resumeItem {
Developed PoS Android app for local shops with \textgreater100 customers as of Dec 2017.
[Kotlin, Java, SQL]
}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------PROJECTS-----------
% \section{Projects}
%    \resumeSubHeadingListStart
%      \resumeProjectHeading
%          {\textbf{Gitlytics} $|$ \emph{Python, Flask, React, PostgreSQL, Docker}}{June 2020 -- Present}
%          \resumeItemListStart
%            \resumeItem{Developed a full-stack web application using with Flask serving a REST API with React as the frontend}
%            \resumeItem{Implemented GitHub OAuth to get data from user’s repositories}
%            \resumeItem{Visualized GitHub data to show collaboration}
%            \resumeItem{Used Celery and Redis for asynchronous tasks}
%          \resumeItemListEnd
%      \resumeProjectHeading
%          {\textbf{Simple Paintball} $|$ \emph{Spigot API, Java, Maven, TravisCI, Git}}{May 2018 -- May 2020}
%          \resumeItemListStart
%            \resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
%            \resumeItem{Published plugin to websites gaining 2K+ downloads and an average 4.5/5-star review}
%            \resumeItem{Implemented continuous delivery using TravisCI to build the plugin upon new a release}
%            \resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
%          \resumeItemListEnd
%    \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}

\hspace*{7pt}
\small{\textbf{Technical skills:} Java, Python, C++, SQL, ElasticSearch, CassandraDB, Spark, CI/CD, distributed systems}
\newline
\hspace*{8pt}
\small{\textbf{Soft skills:} effective communication, critical thinking, problem solving, attention to details, collaboration, autonomy}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Ulsan National Institute of Science and Technology (UNIST)}{Ulsan, South Korea}
{B.S. in Physics and Computer Science}{Sept. 2014 - Aug. 2019}
\resumeItemListStart
\resumeItem{Graduated \textbf{top-5} university in South Korea with \textbf{cum laude honors}}
\resumeItem{Received UNIST Global Dream Scholarship: \textbf{free tuition} + \textbf{\$300 per month} allowance}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------Achievements-----------
\section{Achievements}
\parbox[t]{0.45\textwidth}{
    \begin{itemize}[leftmargin=0.15in, label={}]

    \vspace{-12pt}
    \small{\item{
    \textbf{Asia-Pacific Informatics Olympiad} \\
    \textit{2014 (\textbf{bronze}), 2013 (participant)} \\
    }}

    \vspace{-15pt}
    \small{\item{
    \textbf{Eurasian Informatics Olympiad} \\
    \textit{2013 (\textbf{silver}), 2011 (\textbf{bronze})} \\
    }}

    \end{itemize}
}
\parbox[t]{0.45\textwidth}{
    \begin{itemize}[leftmargin=0.15in, label={}]

        \vspace{-12pt}
        \small{\item{
        \textbf{All-Russian Team Olympiad in Informatics} \\
        \textit{2013 (\textbf{bronze}), 2011 (participant)} \\
        }}

        \vspace{-15pt}
        \small{\item{
        \textbf{Kazakhstan IOI reserves member} \\
        \textit{2012 - 2014} \\
        }}

    \end{itemize}
}

%-------------------------------------------
\end{document}
